{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-11 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, work home sync

\section{Preliminaries}
    Throughout, assume problem of types $F = f + g$ where $f: \RR \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
    We consider optimization problem of the form
    \begin{align*}
        \min_x \left\lbrace
            F(x) \defeq f(x) + g(x)
        \right\rbrace. 
    \end{align*}
    To start we define the following quantities
    \begin{enumerate}
        \item The proximal gradient model function: 
        $$
            \widetilde{\mathcal M}^{L^{-1}}
            (x; y) \defeq
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
            + \frac{L}{2}\Vert x - y\Vert^2. 
        $$
        \item The proximal point model function: 
        $$
            \mathcal M^{L^{-1}}(x; y) := F(x) + \frac{L}{2}\Vert x - y\Vert^2
        $$
        \item The proximal gradient operator $T_L = [I + L^{-1}\partial g]\circ [I - L^{-1}\nabla f]$. Since $L$ is fixed throughout, the subscript may be omitted and become $T$ instead to make the notations simpler. 
    \end{enumerate}
    To state the following lemma, we define the Bregman divergence of $f$ to be 
    \begin{align*}
        D_f(x, y): \RR^n \times \RR^n \rightarrow \RR 
        \defeq f(x) - f(y) - \langle \nabla f(x), x - y\rangle. 
    \end{align*}

@@

    \begin{theorem}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
        Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$. 
        Define scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by: 
        \begin{align*}
            \hat \gamma &:= (1 - \alpha_k)\gamma + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= \hat\gamma^{-1}
            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{theorem}
    \begin{observation}\label{obs:stepwise-wapg}
        Let's observe Definition \ref{def:stepwise-wapg} closely. 
        We make two crucial observations here. 
        With the equalities, we define the following quantities associate with it. 
        Fix any integer $k \ge 0$. 
        To verify, we use the fundamental proximal gradient inequality. 
        Next, observe that we have $x_k, y_k, v_k$ lie on the same line because they have 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
    \end{observation}
        To see (Q1), observe 
        \begin{align*}
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            \\
            \iff 
            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
            &= 
            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
            \\
            \iff 
            y_k &= 
            \frac{
                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
            \\
            &=  
            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
        \end{align*}
        On the first equality (Q1), we multiplied both side of the equation by $\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
        We used the definition of $\hat \gamma$ here. 
        To see the second equality (Q2), consider: 
        \begin{align*}
            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
            \\
            \iff
            y_k - x_k &= 
            (\gamma + \alpha_k \mu)^{-1}
            (\alpha_k \gamma_k v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
            \\
            \iff 
            (\gamma + \alpha_k \mu)(y_k - x_k)
            &= 
            \alpha_k\gamma v_k + 
            (\hat \gamma - \gamma - \alpha_k \mu) x_k
            \\
            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
            \\
            &= \alpha_k \gamma(v_k - x_k)
            \\
            \iff 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line.

    \begin{proposition}[Stepwise lyapunov]\label{prop:stepwise-lyapunov}
        For all $k \ge 0$, given $v_k, x_k, \alpha_k, \gamma_k$, let $\mu \ge 0$ iterates: $y_k, v_{k + 1}, x_{k + 1}, \alpha_{k + 1},\gamma \ge 0$ be given by Definition \ref{def:stepwise-wapg}. 
        Let $F^* = F(x^*)$ where is an arbitrary $x^* \in \RR^n$. 
        If we define $R_{k + 1}$ by some arbitrary $R_k \in \RR^n$: 

@@

            &\defeq 

@@

                L^{-1} - \frac{\alpha_k^2}{\hat\gamma}

@@

                \frac{\mu\alpha_k\gamma}{2\hat\gamma}

@@

        Then we have the inequality: 

@@

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_0 \ge 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, $\textcolor{red}{\rho_k \ge 0}$, $\alpha_k \in (0, 1)$. 
        The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
        \begin{align*}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
                \\
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
    \end{observation}

@@

        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG. 

@@

        \begin{proposition}[R-WAPG intermediate Form I]\label{prop:wapg-intermediate-form}

@@

            Suppose that $(y_i, x_i, v_i)$ are generated by the WAPG algorithm for all $0 \le i \le k$ using sequence $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge0}$ such that for any integer $k\ge 0$, $\alpha_k \in (0, 1)$ and $\rho_k \ge 0$. 
            Then the iterates can be expressed without the sequence $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and they satisfy: 

@@

            The proof of the intermediate form is no complete. 

@@

        \begin{proposition}[WAPG fits similar triangle form]\label{prop:wagp-st-form}
            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.  
            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 
            \begin{align*}
                y_k &= 
                \left(
                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proposition}
        \begin{proof}
            From Proposition \ref{prop:wapg-intermediate-form}, set 
            \begin{align*}
                \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
                \\
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                \\
                (1 + \xi_k)^{-1}\delta_k &= \frac{1}{L\alpha_k}
                \iff L \delta_k = \frac{1 + \xi_k}{\alpha_k}. 
            \end{align*}
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            Hence $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)$. 
            To see, we have 
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Next
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Therefore, substituting it gives: 
            \begin{align*}
                v_{k + 1} &= 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proof}

>>>>

\section{Preliminaries}
    Throughout Section 1, 2, 3, we assume the problem of types $F = f + g$ where $f: \RR \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: Q \rightarrow \overline \RR$ is convex. 
    We consider optimization problem of the form
    \begin{align*}
        \min_x \left\lbrace
            F(x) \defeq f(x) + g(x)
        \right\rbrace. 
    \end{align*}
    To start we define the following quantities
    \begin{enumerate}
        \item The proximal gradient model function: 
        $$
            \widetilde{\mathcal M}^{L^{-1}}
            (x; y) \defeq
            g(x) + f(y) + \langle \nabla f(y), x - y\rangle 
            + \frac{L}{2}\Vert x - y\Vert^2. 
        $$
        \item The proximal point model function: 
        $$
            \mathcal M^{L^{-1}}(x; y) := F(x) + \frac{L}{2}\Vert x - y\Vert^2
        $$
        \item The proximal gradient operator $T_L = [I + L^{-1}\partial g]\circ [I - L^{-1}\nabla f]$. Since $L$ is fixed throughout, the subscript may be omitted and become $T$ instead to make the notations simpler. 
    \end{enumerate}
    To state the following lemma, we define the Bregman divergence of $f$ to be 
    \begin{align*}
        D_f(x, y): \RR^n \times \RR^n \rightarrow \RR 
        \defeq f(x) - f(y) - \langle \nabla f(x), x - y\rangle. 
    \end{align*}

@@

    \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
        Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \ge 0, \gamma \ge 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities: 
        \begin{align*}
            \hat \gamma &:= (1 - \alpha_k)\gamma + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= \hat\gamma^{-1}
            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}\label{obs:stepwise-wapg}
        Let's observe Definition \ref{def:stepwise-wapg} closely. 
        We make two crucial observations here. 
        With the equalities, we define the following quantities associate with it. 
        Fix any integer $k \ge 0$. 
        To verify, we use the fundamental proximal gradient inequality. 
        Next, observe that we have $x_k, y_k, v_k$ lie on the same line because they have 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
    \end{observation}
        To see (Q1), observe 
        \begin{align*}
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            \\
            \iff 
            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
            &= 
            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
            \\
            \iff 
            y_k &= 
            \frac{
                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
            \\
            &=  
            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
        \end{align*}
        On the first equality (Q1), we multiplied both side of the equation by $\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
        We used the definition of $\hat \gamma$ here. 
        To see the second equality (Q2), consider: 
        \begin{align*}
            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
            \\
            \iff
            y_k - x_k &= 
            (\gamma + \alpha_k \mu)^{-1}
            (\alpha_k \gamma_k v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
            \\
            \iff 
            (\gamma + \alpha_k \mu)(y_k - x_k)
            &= 
            \alpha_k\gamma v_k + 
            (\hat \gamma - \gamma - \alpha_k \mu) x_k
            \\
            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
            \\
            &= \alpha_k \gamma(v_k - x_k)
            \\
            \iff 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line.

    \begin{proposition}[Stepwise lyapunov]\label{prop:stepwise-lyapunov}\;\\
        Fix any integer $k \ge0$, suppose that $v_{k + 1}, x_{k + 1}, y_k, g_k, \gamma, \hat \gamma$ satisfies Definition \ref{def:stepwise-wapg}. 
        Given any $R_k$.
        Define: 

@@

            \defeq

@@

@@

@@

        Then it has for all $x^* \in \RR^n$ where $F^* = F(x^*)$, the inequality: 

@@

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_0 \in [0, 1]$, $(x_0, v_0)$ or equivalently: $(x_0, y_0), (y_0, v_0)$. 
        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 0$: 
        $$
        \begin{aligned}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \text{find }&\alpha_k \in [0, 1], \rho_k \ge 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 \le \rho_k \alpha_k^2 \le 1, 
            \hat \gamma_{k + 1} &:= L\alpha_k^2, 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            g_k &= \mathcal G_L y_k, 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            x_{k + 1} &= T_L y_k. 
        \end{aligned}
        $$
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
    \end{observation}
    \begin{observation}\label{obs:r-wapg-observation-1}
        The sequence $\alpha_k$ satisfies the condition that $\alpha_k \in [0, 1]$.
        In addition, if $\alpha_0 \in (0, 1)$, then the entire sequence $\alpha_k \in (0, 1)$. 
        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in [0, 1]$ and $\rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates 
        $$
        \begin{aligned}
            \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \pm
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
        \end{aligned}
        $$
        Choosing the positive sign which is the larger one of the roots of the quadratic. 
        We have $\alpha_k \ge 0$ because: 
        $$
        \begin{aligned}
            \alpha_k &=
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
            & \ge 0. 
        \end{aligned}
        $$
        If $\alpha> 0$, we would have $4\rho_{k - 1} \alpha_{k - 1}^2 > 0$ , which allows for $> 0$ instead. 
        An upper bound can be identified by using inductive hypothesis and consdering: 
        $$
        \begin{aligned}
            \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
                \frac{\mu}{L} - 1
                \sqrt{(1 - \mu/L)^2 + 4}
            &\le \frac{1}{2}\left(
                0 + \sqrt{0 + 4}
            \right) = 1. 
        \end{aligned}
        $$
        Going from the second to the third inequality, we maximized $\mu/L$ by monotonicity of the linear function and the square root function. 
        Therefore, inductively, $\alpha_k \in [0, 1]$ holds. 
        Additionally, if $\alpha_{k - 1} \in (0, 1)$, then the results can be strengthened and $\alpha_k \in (0, 1)$ as well.

    \end{observation}

@@

        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 

@@

        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\

@@

            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$. 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge0}, (\rho_k)_{k\ge0}$, and for all $k\ge 0$ they are algebraically equivalent to

@@

            The is now complete. 

@@

        \begin{definition}[R-WAPG intermediate representation]\label{def:r-wapg-intermediate}\;\\
            Given any initial $\alpha_0 \in (0, 1)$, $(x_0, y_0)$ or equivalently $(x_0, v_0), (y_0, v_0)$. 
            Assume that the auxiliary sequence $\rho_k$ has $\rho_k \alpha_k^2 < 1$ for all $k \ge 0$. 
            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by 
            $$
            \begin{aligned}
                \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \end{aligned}
            $$
        \end{definition}
        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.  
            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            From Definition \ref{def:r-wapg-intermediate}, set 
                \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                (1 + \xi_k)^{-1}\delta_k &= \frac{1}{L\alpha_k}
                \iff L \delta_k = \frac{1 + \xi_k}{\alpha_k}. 
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            Hence $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)$. 
            To see, we have 
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                &= \frac{L}{L\alpha_k - \mu}. 
            Next
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                &= \frac{L}{L\alpha_k - \mu}. 
            Therefore, substituting it gives: 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
